The SMT Competition 2015--2018

### 2018-10-21 2018/report/SMT-COMP.tex
Infrastructure

    \node [rotate=90] at (-1.5,2.7) {\small Number of benchmarks};

@@

There are slightly fewer divisions than logics in the SMT Library
(Table~\ref{table:smtlib}) because not every logic contains benchmarks
eligible for the competition.  Some benchmarks typically have to be
excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
were excluded because they contained partial or underspecified
operations (e.g., bit-vector division) whose precise semantics were
being debated at the time.  Additionally in 2016, one benchmark was
excluded because it contained incorrect status information.  In 2017,
1,104 benchmarks were excluded because their logic had been classified
incorrectly, and 8 benchmarks were excluded because of incorrect or
missing status information.  Moreover, divisions containing datatypes
({\tt DT})---which were new in~2017---were excluded from the
unsat-core track because of lacking tool support.  In 2018, 3,603
benchmarks were excluded because they contained named terms (a feature
of the SMT-LIB language that is not permitted in competition
benchmarks), and 5 benchmarks were excluded because of missing status
information.

@@

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation found that this ``significantly lessens the
ability of a competition to determine `best'
solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
increased computational resources available for the competition since
its move to StarExec, this prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible
benchmarks. \TODO: benchmark weights

@@

\section{StarExec}
\label{sec:starexec}

@@

>>>>

    \node [rotate=90] at (-1.5,2.7) {\small Benchmarks};

@@

There are slightly fewer divisions than logics in the SMT Library
(Table~\ref{table:smtlib}) because not every logic contains benchmarks
eligible for the competition.  Some benchmarks typically have to be
excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
were excluded because they contained partial or underspecified
operations (e.g., bit-vector division) whose precise semantics were
being debated at the time.  Additionally in 2016, one benchmark was
excluded because it contained incorrect status information.  In 2017,
1,104 benchmarks were excluded because their logic had been classified
incorrectly, and 8 benchmarks were excluded because of incorrect or
missing status information.  Moreover, divisions containing datatypes
({DT})---which were new in~2017---were excluded from the unsat-core
track because of lacking tool support.  In 2018, 3,603 benchmarks were
excluded because they contained named terms (a feature of the SMT-LIB
language that is not permitted in competition benchmarks), and 5
benchmarks were excluded because of missing status information.

@@

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers.''~\cite{DBLP:journals/jar/CokSW15} Together with the
increased computational resources available to the competition since
its move to StarExec, this prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible
benchmarks. \TODO: benchmark weights

@@

\section{Infrastructure}
\label{sec:starexec}

Since 2014 (and previously for the evaluation in
2013~\cite{DBLP:journals/jar/CokSW15}), the computational workload of
the competition is being run on StarExec, a ``cross-community
infrastructure for logic solving''~\cite{DBLP:conf/cade/StumpST14}
developed at the University of Iowa and supported by the National
Science Foundation.  Each machine in the StarExec cluster is equipped
with two E5-2609 Intel Xeon processors (10~MiB Cache, 2.4~GHz).  This
hardware configuration has been unchanged since~2013.  Up to two
solvers are run simultaneously on each machine: one solver on each
processor, with four cores available.  Memory usage is limited
to~60~GiB per solver.

On the software side, the cluster is running Red Hat Enterprise Linux
Workstation.  The~2015 competition was running on release~6.3
(Santiago, kernel 2.6.32-431).  This was updated to~7.2 (Maipo, kernel
3.10.0-327) before the~2016 competition, and the kernel was further
updated to~3.10.0-514 before the~2017 competition.  The platform
emphasizes stability over bleeding edge technology.  This has on
occasion caused problems with solver binaries that had been compiled
on other Linux distributions and linked against library versions not
(yet) available on the cluster.  Usually, such problems are easily
solved by building the solver on StarExec instead.  The StarExec
developers have made a virtual machine image available to facilitate
this and similar tasks.

Interaction with StarExec is mostly via its web interface,
\url{https://www.starexec.org}.  The interface allows registered users
to upload and share benchmarks and solvers, to create and manage jobs
that apply selected solvers to a selection of benchmarks, and to view
and download job results.  Other features, such as pre-processing of
benchmarks (e.g., for scrambling) and post-processing of solver
output, are also supported.

Jobs consist of individual \emph{job pairs}.  Each job pair
corresponds to a specific solver-benchmark combination.
Figure~\ref{fig:job-pairs} shows the total number of job pairs for the
SMT Competition from~2015 to~2018.  Over this period, the number has
grown by~72\,\%, from~1,028,615 job pairs in~2015 to~1,776,062 job
pairs in~2018.  (This is the number of unique solver-benchmark
combinations that were part of the competition.  The number of job
pairs that were actually run is even higher: test jobs and job pairs
that had to be re-run, e.g., because of issues with the StarExec
infrastructure, are not included.)  For comparison, the~2014
competition only ran~339,714 job
pairs~\cite{DBLP:journals/jsat/CokDW14}.

Also shown in Figure~\ref{fig:job-pairs} is the total wall-clock time
(summed over all job pairs) for the competition.  This has more than
doubled, from 3.5~years in~2015 to 7.6~years in~2018.  (These are
solver run-times only.  Time that the cluster spent on pre- and
post-processing of benchmarks and solver output or on other auxiliary
tasks is not included.)  The increase in~2016 is largely due to the
inclusion of non-incremental benchmarks with unknown status; these
were evaluated with a wall-clock time limit of 10~minutes.  In~2017,
when these benchmarks had become eligible for the main track,
main-track job pairs were first run with a time limit of 10~minutes;
when it became apparent to the organizers that there were sufficient
resources to increase this limit, job pairs that had timed out were
re-run with a time limit of 20~minutes.  Table~\ref{table:time-limits}
shows the wall-clock time limits that were imposed for each track and
year.

\begin{table}
  \caption{Wall-clock time limits}
  \label{table:time-limits}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    Main track        & 40\,min & 40\,min & 20\,min & 20\,min \\
    Application track & 40\,min & 40\,min & 40\,min & 40\,min \\
    Unsat-core track  &      -- & 40\,min & 40\,min & 40\,min \\
    \hline
  \end{tabular}
\end{table}

StarExec typically reserves between~80 and~150 machines for the SMT
Competition, allowing its workload to be completed within two to three
weeks.  By these measures, the SMT Competition has become not only one
of the heaviest users of StarExec, but also one of the largest
competitions in automated reasoning.

\begin{figure}
  \centering
  \begin{tikzpicture}
    \draw [gray] (0,0) -- (12,0);
    \draw [gray] (0,1.5) -- (12,1.5);
    \draw [gray] (0,3) -- (12,3);
    \draw [gray] (0,4.5) -- (12,4.5);
    \draw [gray] (0,6) -- (12,6);

    \node [left] at (0,0) {\footnotesize 0};
    \node [left] at (0,1.5) {\footnotesize 500,000};
    \node [left] at (0,3) {\footnotesize 1,000,000};
    \node [left] at (0,4.5) {\footnotesize 1,500,000};
    \node [left] at (0,6) {\footnotesize 2,000,000};

    \node [rotate=90] at (-2,3) {\small Job pairs};

    \node [right] at (12,0) {\footnotesize 0};
    \node [right] at (12,1.5) {\footnotesize 2};
    \node [right] at (12,3) {\footnotesize 4};
    \node [right] at (12,4.5) {\footnotesize 6};
    \node [right] at (12,6) {\footnotesize 8};

    \node [rotate=-90] at (12.9,3) {\small Wall-clock time (years)};

    \draw [fill=black] (1,0) rectangle (2,3.085845); % 1,028,615
    \draw [fill=black] (3.75,0) rectangle (4.75,4.687632); % 1,562,544
    \draw [fill=black] (6.5,0) rectangle (7.5,4.366839); % 1,455,613
    \draw [fill=black] (9.25,0) rectangle (10.25,5.328186); % 1,776,062

    \draw [fill=white] (2,0) rectangle (3,2.6088709094); % 3,4784945459
    \draw [fill=white] (4.75,0) rectangle (5.75,4.3030490392); % 5,7373987189
    \draw [fill=white] (7.5,0) rectangle (8.5,5.6286127759); % 7,5048170345
    \draw [fill=white] (10.25,0) rectangle (11.25,5.7280186691); % 7,6373582255

    \node [below] at (2,0) {\footnotesize 2015};
    \node [below] at (4.75,0) {\footnotesize 2016};
    \node [below] at (7.5,0) {\footnotesize 2017};
    \node [below] at (10.25,0) {\footnotesize 2018};
  \end{tikzpicture}
  \caption{Number of job pairs ($\blacksquare$) and total wall-clock time ($\square$).}
  \label{fig:job-pairs}
\end{figure}

The StarExec infrastructure has been vitally important in allowing the
competition to grow to its current size.  The competition organizers
have given the StarExec developers comprehensive feedback, and filed
dozens of feature requests and bug reports since~2013.  The
infrastructure has become increasingly stable; serious issues are now
rare.  When they did surface during an ongoing competition, they
received a swift response by the StarExec team (under the lead of
Aaron Stump).  This has been critical to the success of the
competition on more than one occasion.

@@

inclusion of check-sat commands with unknown status in the application track

competition-wide rankings for application and unsat-core track

more benchmarks, especially for underrepresented (i.e., small) logics
